### 2013-09-25 evaluation/paper.tex
work on evaluation blub

\subsection{Experiments using Exact Inference}
In this section, we present results on multi-class classification, sequence
labeling and multi-label prediction. In these
tasks, exact inference is possible, and we can compute the exact objective of
the various algorithms easily. We use the dynamic programming algorithm
implemented in \textsc{OpenGM} for experiments for the tree and chain models.
For the full pairwise multi-label model, we use branch-and-bound together with the %FIXME AD3 solver description?
We found that using the linear programming relaxation on the multi-label
dataset is often tight, and there was no need to resort to approximate
inference.

@@

Next, we consider the multi-label task, starting with the tree-shaped models.
The results for the yeast and scene datasets are shown in \Figref{multi-label-results},
respectively. The caching $1$-slack algorithm is much faster than the
non-caching one on both datasets. While the two variants of the $n$-slack algorithm are equally
fast with respect to passes over the training data, solving the QP every 100 steps is among the
fastest algorithms, while solving the QP every step is among the slowest.

@@

\subsection{Experiments using Approximate Inference}
For the remaining tasks of multi-label classification with the full graph, the
snakes dataset and image segmentation, exact inference is usually not possible.

We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and AD$^3$, a dual-subgradient method to solve the LP
relaxation of the inference problem.
Evaluation of algorithms where exact inference is not possible is much harder,
as it is usually not possible to evaluate the exact objective. When using AD$^3$,
we can still consider the relaxed task, which will be solved exactly in the
majority of cases (AD$^3$ can fail to find the primal solution to the LP
relaxation).
When using fusion moves, there is no obvious interpretation of the produced
primal objective, other than that it provides a lower bound of the actual
objective. Nevertheless, we find it informative to analyze the behavior of this
lower bound.

@@

>>>>

\subsection{Experiments using Exact Inference}
In this section, we present results on multi-class classification, sequence
labeling and multi-label prediction. In these
tasks, exact inference is possible, and we can compute the exact objective of
the various algorithms easily. We use the dynamic programming algorithm
implemented in \textsc{OpenGM} for experiments for the tree and chain models.
For the full pairwise multi-label model, we use branch-and-bound together with the %FIXME AD3 solver description?
We found that using the linear programming relaxation on the scene dataset is
often tight, and there was no need to resort to approximate inference. Inference
on the yeast dataset was more complex, and on the verge of being non-practical.
We use this dataset as an example for very cosly inference.

@@

Next, we consider the multi-label task.  The results for the yeast and scene
datasets are shown in \Figref{multi-label-results}, respectively. The caching
$1$-slack algorithm is much faster than the non-caching one on both datasets.
While the two variants of the $n$-slack algorithm are equally fast with respect
to passes over the training data, solving the QP every 100 steps is among the
fastest algorithms, while solving the QP every step is among the slowest.

@@

\subsection{Experiments using Approximate Inference}
For the remaining tasks of the snakes dataset and image segmentation, exact
inference is intractable for learning.

We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and the linear programming relaxation provided by AD$^3$,
not using branch-and-bound.

Evaluation of algorithms where exact inference is not possible is much harder,
as it is usually not possible to evaluate the exact objective. When using AD$^3$,
we can still consider the relaxed task, which will be solved exactly in the
majority of cases (AD$^3$ can fail to find the primal solution to the LP
relaxation).
When using fusion moves, there is no obvious interpretation of the produced
primal objective, other than that it provides a lower bound of the actual
objective. Nevertheless, we find it informative to analyze the behavior of this
lower bound.

@@

\Figref{snakes_results} shows the results on the snakes dataset.
The top row shows the objective when learning with fusion-moves, the next row the training set loss.
First, we notice that even the approximate
